---
title: "Foundation lab 2 - Badge"
author: ""
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The final activity for each learning lab provides space to work with data and to reflect on how the concepts and techniques introduced in each lab might apply to your own research.

To earn a badge for each lab, you are required to respond to a set of prompts for two parts: 

-   In Part I, you will reflect on your understanding of key concepts and begin to think about potential next steps for your own study.

-   In Part II, you will create a simple data product in R that demonstrates your ability to apply a data analysis technique introduced in this learning lab.

### Part I: Reflect and Plan

Use the institutional library (e.g. [NCSU Library](https://www.lib.ncsu.edu/#articles)), [Google Scholar](https://scholar.google.com/) or search engine to locate a research article, presentation, or resource that applies learning analytics analysis to an educational context or topic of interest. More specifically, **locate a study that makes use of one of the data structures we learned today.** You are also welcome to select one of your research papers.

1.  Provide an APA citation for your selected study.

    -   

2.  What educational issue, “problem of practice,” and/or questions were addressed?

    -   


3.  Briefly describe any steps of the data-intensive research workflow that detailed in your article or presentation. 



    -   

4.  What were the key findings or conclusions? What value, if any, might education practitioners find in these results?


    -   

5.  Finally, how, if at at, were educators in your self-selected article involved prior to wrangling and analysis?
    -   

Draft a new research question of guided by the the phases of the Learning Anlytics Workflow. Or use one of your current research questions.

1.  What educational issue, “problem of practice,” and/or questions is  addressed??

    -   

2.  Briefly describe any steps of the data-intensive research workflow that can be detailed in your article or presentation.
 


3.  How, if at all, will your article touch upon the application(s) of LA to “understand and improve learning and the contexts in which learning occurs?”
    -   

### Part II: Data Product

In our Learning Analytics code-along, we only scratched the surface on the number of ways that we can wrangle the data.

Using one of the data sets provided in the data folder, your goal for this lab is to extend the Learning Analytics Workflow from our code-along by preparing and wrangling different data. You can use one of the data sets in the data folder or alternatively, you may use your own data set to use in the workflow. 

We will be continuing on in the next sessions where you can continue to use the data started in this badge if desires.

I highly recommend creating a new R script in your lab-2 folder to complete this task. When your code is ready to share, use the code chunk below to share the final code for your model and answer the questions that follow.

```{r, my-data-product}
# YOUR FINAL CODE HERE
```

### Knit & Submit

Congratulations, you've completed your Foundation Badge on Learning Analytics Workflow! Complete the following steps to submit your work for review by

1.  Click the yarn icon above to "knit" your data product to a [HTML](https://bookdown.org/yihui/rmarkdown/html-document.html) file that will be saved in your R Project folder.

2.  Commit your changes in GitHub Desktop and push them to your online GitHub repository.

3.  Locate and copy the link to your GitHub web page ([See here for instructions](https://towardsdatascience.com/how-to-create-a-free-github-pages-website-53743d7524e1)).

4.  Post a new discussion on GitHub to our [SNA Badges forum](https://github.com/orgs/laser-institute/teams/network-analysis/discussions/1). In your post, include a link to your published web page and a short reflection highlighting one thing you learned from this lab and one thing you'd like to explore further.
