---
title: "dataproducts_codealong"
author: "Jeanne McClure"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Prepare

Install and load library's needed for analysis.
```{r}
#load libraries
library(tidyverse)
library(here)
```

## 2. Wrangle

Read in previously saved data
```{r}
# read in data to explore 
data_to_explore <- read_csv(here("data", "data_to_explore.csv"))

```


## Explore
Looked at insights using ggplot
What insights did we find?

## Model
Quantify the insights using mathematical models.

#### A. MATHMATICAL

Does time spent predict grade earned?

```{r}
# Use linear regression model
lm(proportion_earned ~ time_spent_hours, 
   data = data_to_explore)
```

```{r}
# Add predictor variable for science
lm(proportion_earned ~ time_spent_hours + int, 
   data = data_to_explore)

# save the model
m1 <- lm(proportion_earned ~ time_spent_hours + int, data = data_to_explore)

```

Run a summary model for the model you just created called, `m1.`
```{r}
#run the summary
summary(m1)

```

```{r}
#install apaTables if this is your first time - do you remember how?

#load packages
library(apaTables)
# use the {apaTables} package to create a nice regression table that could be used for later publication.
apa.reg.table(m1, filename = "lm-table.doc")

```

## Communicate
What are your findings?